---
title: "Experiment 3 Hindu participants' beliefs about knowledge"
output: html_notebook
---

```{r}
rm(list = ls(all = TRUE))
#load needed libraries
library(FactoMineR)
library(psych)
library(gdata)
library(data.table)
library(tidyr)
library(reshape2)
library(ggfortify)
library(qdapTools)
library(lm.beta)

##### change current group to select dataset
##### note:separate scripts for Experiments 3 and 4b
currentgroup = c("US","JP")
currentcondition = c(2)

## prep; load data files & set parameters
masterdata  = read.table(file = "/Users/jennywang/Google Drive/Museum/mathitude/data/alternative analyses/mathitudemaster jp.csv", sep=",",header=TRUE, na.strings="")
data = subset(masterdata,masterdata$Group %in% currentgroup)
data = subset(data,data$Experiment %in% currentcondition)
data_t = data
data_t[,24:37]=(as.numeric(data[,24:37]=="T"|data[,24:37]=="O"))

cols<- c(a.born="royalblue1",b.mature="skyblue2",c.teach="darkorange1",d.observe="orange")

read <- c("how.read")
sensory <- c("how.see","how.hear")
core <- c("how.color","how.depth","how.face","how.gravity","how.objperm","how.number","how.help")
types <- c("read","sensory","core")

allitems <-c("read","help","number","objperm","gravity","face","depth","color","hear","see")
allhows <-c("how.read","how.help","how.number","how.objperm","how.gravity","how.face","how.depth","how.color","how.hear","how.see")

allwhen<-c("when.read","when.help","when.number","when.objperm","when.gravity","when.face","when.depth","when.color","when.hear","when.see")
empirical = c(6, 0.5, 0.0055,0.29, 0.25, 0.0019, 0.0054, 0.33, 0.0027, 0.052)


```

```{r}
# ## PCA ######### ########### cluster analysis ###########
pcadata=data_t[,24:33] #mturk how
pcadata=na.omit(pcadata)
pcadata=t(pcadata)
autoplot(prcomp(pcadata), label=TRUE)

```

```{r}
av.emp = mean(c(0.5, 0.0055,0.29, 0.25, 0.0019, 0.0054, 0.33))
how.summ = data_t[,c(1:9,38,39,40,41)]
output = data.frame(files=NULL)
summ.output = data.frame(files=NULL)
for(i in c(1:nrow(data_t))){
  how.sub = how.summ[i,]
  sum.sub = as.data.frame(lapply(how.sub, rep, 3))
  how.sub = as.data.frame(lapply(how.sub, rep, 10))
  for (k in c(1:10)){
    how.sub$Item[k] <- allhows[k]
    how.sub$How[k] <- data_t[[paste("how.",allitems[k],sep="")]][i]
    how.sub$When[k] <- data_t[[paste("when.",allitems[k],sep="")]][i]
    how.sub$When.estimate[k]<-0.13*exp(0.78*how.sub$When[k])
    }
  for(j in c(1:3)){
    sum.sub$Type[j]<-types[j]
    sum.sub$How[j] <- mean(how.sub$How[how.sub$Item %in% eval(parse(text = types[j]))],na.rm=TRUE)
    sum.sub$When[j] <- mean(how.sub$When[how.sub$Item %in% eval(parse(text = types[j]))],na.rm=TRUE)
    sum.sub$When.estimate[j]<-mean(how.sub$When.estimate[how.sub$Item %in% eval(parse(text = types[j]))],na.rm=TRUE)
  }
  output = rbind(output,how.sub)
  summ.output = rbind(summ.output,sum.sub)
}

descr.how <-describeBy(summ.output$How,list(summ.output$Type),na.rm=TRUE,mat=TRUE)
descr.how$confIV1 = descr.how$mean-1.96*descr.how$se
descr.how$confIV2 = descr.how$mean+1.96*descr.how$se

descr.how[,c(2,5,16,17)]
```
```{r}
descr.when <-describeBy(summ.output$When,list(summ.output$Group,summ.output$Type),na.rm=TRUE,mat=TRUE)
descr.when$confIV1 = descr.when$mean-1.96*descr.when$se
descr.when$confIV2 = descr.when$mean+1.96*descr.when$se

descr.when$mean.estimate = 0.13*exp(0.78*descr.when$mean)
descr.when$se.estimate = 0.13*exp(0.78*descr.when$se)
descr.when$confIV1.estimate = descr.when$mean.estimate-1.96*descr.when$se.estimate
descr.when$confIV2.estimate = descr.when$mean.estimate+1.96*descr.when$se.estimate

descr.when[,c(2,3,6,19:22)]

```

```{r}
descr.when$mean.estimate[1]/av.emp
```




```{r}
## calculate group stats for sensory, core knowledge, and read

summ.output$Condition = as.factor(as.character(summ.output$Condition))
summ.output$Type = as.factor(as.character(summ.output$Type))
summ.output$Gender = as.factor(as.character(summ.output$Gender))
summ.output$Parent = as.factor(as.character(summ.output$Parent))
summ.output$SubID = as.factor(as.character(summ.output$SubID))
summ.output$Education = as.factor(as.character(as.integer(summ.output$Education)>1))

descr.how <-describeBy(summ.output$How,list(summ.output$Group,summ.output$Type),na.rm=TRUE,mat=TRUE)
descr.how$confIV1 = descr.how$mean-1.96*descr.how$se
descr.how$confIV2 = descr.how$mean+1.96*descr.how$se

descr.how


```


```{r}
output.core=subset(summ.output,summ.output$Type=="core")
t.test(output.core$How,mu=0.5)

output.sensory = subset(summ.output,summ.output$Type=="sensory")
output.read = subset(summ.output,summ.output$Type=="read")

```

```{r}
######### linear regression ###########
fit.lm <- lm(When.estimate~Group+Gender+Age,data=output.core)
lm.beta(fit.lm)
```

```{r}
summary(fit.lm)
```

```{r}
fit.lm <- lm(When.estimate~Group+Gender+Age,data=output.read)
lm.beta(fit.lm)
```

```{r}
summary(fit.lm)
```

```{r}
fit.lm <- aov(When.estimate~Group,data=output.sensory)
lm.beta(fit.lm)
```

```{r}
summary(fit.lm)

t.test(When.estimate~Group,data=output.sensory)
```





```{r}

fit.lm <- lm(How~Group*Gender+Age,data=output.core)
lm.beta(fit.lm)
```

```{r}
summary(fit.lm)

```

```{r}
summ.h <- describeBy(output.core$How,output.core$Group,na.rm=TRUE,mat=TRUE)
summ.h$confIV1 = summ.h$mean-1.96*summ.h$se
summ.h$confIV2 = summ.h$mean+1.96*summ.h$se
summ.h[,c(2,5,16,17)]
```

```{r}
summ.h <- describeBy(output.core$How,output.core$Gender,na.rm=TRUE,mat=TRUE)
summ.h$confIV1 = summ.h$mean-1.96*summ.h$se
summ.h$confIV2 = summ.h$mean+1.96*summ.h$se
summ.h[,c(2,5,16,17)]
```

```{r}
### overall descriptives based on timeline choices and proportion responses for plotting
des_m = describeBy(data[data$Group=="JP",],group=NULL,na.rm=TRUE)
dat_m = data[data$Group=="JP",24:33]
table_m= mtabulate(dat_m)
time_m = des_m[10:19,]
rownames(time_m) <- c("read","help","number","objperm","gravity","face","depth","color","hear","see")
how_m = table_m/rowSums(table_m,na.rm=FALSE)
colnames(how_m) <- c("b.mature","a.born","d.observe","c.teach")
summ_m = cbind(time_m,how_m)
summ_m$Category = rownames(summ_m)
summ_m$Category.num = c(10,9,8,7,6,5,4,3,2,1)
##age estimates based on actual findings
summ_m$emp.age = empirical
##converting timeline choice mean/se to age estimate
summ_m$mean.estimate = 0.13*exp(0.78*summ_m$mean)
summ_m$se.estimate = 0.13*exp(0.78*summ_m$se)
summ_m$confIV1.estimate = summ_m$mean.estimate-1.96*summ_m$se.estimate
summ_m$confIV2.estimate = summ_m$mean.estimate+1.96*summ_m$se.estimate

summ_JP = summ_m
summ_JP$Group = rep("JP",nrow(summ_JP))

des_m = describeBy(data[data$Group=="US",],group=NULL,na.rm=TRUE)
dat_m = data[data$Group=="US",24:33]
table_m= mtabulate(dat_m)
time_m = des_m[10:19,]
rownames(time_m) <- c("read","help","number","objperm","gravity","face","depth","color","hear","see")
how_m = table_m/rowSums(table_m,na.rm=FALSE)
colnames(how_m) <- c("b.mature","a.born","d.observe","c.teach")
summ_m = cbind(time_m,how_m)
summ_m$Category = rownames(summ_m)
summ_m$Category.num = c(10,9,8,7,6,5,4,3,2,1)
##age estimates based on actual findings
summ_m$emp.age = empirical
##converting timeline choice mean/se to age estimate
summ_m$mean.estimate = 0.13*exp(0.78*summ_m$mean)
summ_m$se.estimate = 0.13*exp(0.78*summ_m$se)
summ_m$confIV1.estimate = summ_m$mean.estimate-1.96*summ_m$se.estimate
summ_m$confIV2.estimate = summ_m$mean.estimate+1.96*summ_m$se.estimate

summ_US = summ_m
summ_US$Group = rep("US",nrow(summ_US))

summ_all = rbind(summ_JP,summ_US)

#all_descrep$group2=as.numeric(all_descrep$group2)

ggplot(data=summ_all,aes(x=Category,y=mean.estimate, color=Group))+
  geom_point(stat="identity", size=3)+
  #geom_line(data=sigfitdata,aes(x=value,y=predict))+
  geom_errorbar(data=summ_all,aes(ymin=confIV1.estimate,ymax=confIV2.estimate),alpha=0.3)+
  labs(y="Age Estimate\n", x="\nCategory")+
  #scale_y_continuous(labels = scales::percent, limits=c(0,1))+
  theme_classic()+
  theme(legend.position="top",
        legend.text=element_text(size=14),
        axis.text=element_text(size=14),
        axis.title=element_text(size=16,face="bold"))

```

```{r}
############### PLOT ##############
library(plotrix)

y=c(0,0.5,1,1.5,2,2.5,3,3.5,4,4.5,5,5.5)
x=c(-0.5:10.5)
colors1 = c("royalblue1","skyblue2","orange","darkorange1")
colors2 = c("royalblue3","skyblue4","orange3","darkorange4")

#colors = c("royalblue2","skyblue3","orange2","darkorange2")
#colors = c("seagreen4","seagreen3","pink2","hotpink")
startpos = pi+(0.2*2*pi/2)
y=c(0.41,0.82,1.23,1.64,2.05,2.45,2.86,3.27,3.68,4.09,4.5,5)
#pdf("JPUS pie.outlined.pdf",width=8,height=8)
plot(x,y,type = "n",xlab="Category",ylab="Timeline",xlim=c(-0.5,12),ylim=c(-0.5,6),axes=TRUE)
axis(side=1,at = summ_JP$Category.num,labels = summ_JP$Category)
axis(side=4)
#animals
floating.pie(summ_US$Category.num[1],summ_US$mean[1],c(summ_US$a.born[1],summ_US$b.mature[1],summ_US$d.observe[1],summ_US$c.teach[1]),
             radius = 0.4,col=colors1,startpos = startpos+0.2,border=NA)
floating.pie(summ_US$Category.num[2],summ_US$mean[2],c(summ_US$a.born[2],summ_US$b.mature[2],summ_US$d.observe[2],summ_US$c.teach[2]),
             radius = 0.4,col=colors1,startpos = startpos-0.1,border=NA)
floating.pie(summ_US$Category.num[3],summ_US$mean[3],c(summ_US$a.born[3],summ_US$b.mature[3],summ_US$d.observe[3],summ_US$c.teach[3]),
             radius = 0.4,col=colors1,startpos = startpos-1.2,border=NA)
floating.pie(summ_US$Category.num[4],summ_US$mean[4],c(summ_US$a.born[4],summ_US$b.mature[4],summ_US$d.observe[4],summ_US$c.teach[4]),
             radius = 0.4,col=colors1,startpos = startpos-1.4,border=NA)
floating.pie(summ_US$Category.num[5],summ_US$mean[5],c(summ_US$a.born[5],summ_US$b.mature[5],summ_US$d.observe[5],summ_US$c.teach[5]),
             radius = 0.4,col=colors1,startpos = startpos-0.4,border=NA)
floating.pie(summ_US$Category.num[6],summ_US$mean[6],c(summ_US$a.born[6],summ_US$b.mature[6],summ_US$d.observe[6],summ_US$c.teach[6]),
             radius = 0.4,col=colors1,startpos = startpos-1.8,border=NA)
floating.pie(summ_US$Category.num[7],summ_US$mean[7],c(summ_US$a.born[7],summ_US$b.mature[7],summ_US$d.observe[7],summ_US$c.teach[7]),
             radius = 0.4,col=colors1,startpos = startpos-1.9,border=NA)
floating.pie(summ_US$Category.num[8],summ_US$mean[8],c(summ_US$a.born[8],summ_US$b.mature[8],summ_US$d.observe[8],summ_US$c.teach[8]),
             radius = 0.4,col=colors1,startpos = startpos-pi/2,border=NA)
floating.pie(summ_US$Category.num[9],summ_US$mean[9],c(summ_US$a.born[9],summ_US$b.mature[9],summ_US$d.observe[9],summ_US$c.teach[9]),
             radius = 0.4,col=colors1,startpos =startpos-pi/5,border=NA)
floating.pie(summ_US$Category.num[10],summ_US$mean[10],c(summ_US$a.born[10],summ_US$b.mature[10],summ_US$d.observe[10],summ_US$c.teach[10]),
             radius = 0.4,col=colors1,startpos = startpos+pi/3,border=NA)
#points(summ_h$Category.num,summ_h$mean,pch=19,col=alpha("red",0.3),cex=5.6)
##human
floating.pie(summ_JP$Category.num[1],summ_JP$mean[1],c(summ_JP$a.born[1],summ_JP$b.mature[1],summ_JP$d.observe[1],summ_JP$c.teach[1]),
             radius = 0.4,col=colors2,startpos = startpos,border=NA)
floating.pie(summ_JP$Category.num[2],summ_JP$mean[2],c(summ_JP$a.born[2],summ_JP$b.mature[2],summ_JP$d.observe[2],summ_JP$c.teach[2]),
             radius = 0.4,col=colors2,startpos = startpos+pi/4,border=NA)
floating.pie(summ_JP$Category.num[3],summ_JP$mean[3],c(summ_JP$a.born[3],summ_JP$b.mature[3],summ_JP$d.observe[3],summ_JP$c.teach[3]),
             radius = 0.4,col=colors2,startpos = startpos+0.2,border=NA)
floating.pie(summ_JP$Category.num[4],summ_JP$mean[4],c(summ_JP$a.born[4],summ_JP$b.mature[4],summ_JP$d.observe[4],summ_JP$c.teach[4]),
             radius = 0.4,col=colors2,startpos = startpos,border=NA)
floating.pie(summ_JP$Category.num[5],summ_JP$mean[5],c(summ_JP$a.born[5],summ_JP$b.mature[5],summ_JP$d.observe[5],summ_JP$c.teach[5]),
             radius = 0.4,col=colors2,startpos = startpos-pi/6,border=NA)
floating.pie(summ_JP$Category.num[6],summ_JP$mean[6],c(summ_JP$a.born[6],summ_JP$b.mature[6],summ_JP$d.observe[6],summ_JP$c.teach[6]),
             radius = 0.4,col=colors2,startpos = startpos,border=NA)
floating.pie(summ_JP$Category.num[7],summ_JP$mean[7],c(summ_JP$a.born[7],summ_JP$b.mature[7],summ_JP$d.observe[7],summ_JP$c.teach[7]),
             radius = 0.4,col=colors2,startpos = startpos-pi/6,border=NA)
floating.pie(summ_JP$Category.num[8],summ_JP$mean[8],c(summ_JP$a.born[8],summ_JP$b.mature[8],summ_JP$d.observe[8],summ_JP$c.teach[8]),
             radius = 0.4,col=colors2,startpos = startpos-pi/6,border=NA)
floating.pie(summ_JP$Category.num[9],summ_JP$mean[9],c(summ_JP$a.born[9],summ_JP$b.mature[9],summ_JP$d.observe[9],summ_JP$c.teach[9]),
             radius = 0.4,col=colors2,startpos = startpos,border=NA)
floating.pie(summ_JP$Category.num[10],summ_JP$mean[10],c(summ_JP$a.born[10],summ_JP$b.mature[10],summ_JP$d.observe[10],summ_JP$c.teach[10]),
             radius = 0.4,col=colors2,startpos = startpos+pi/3,border=NA)
par(bg=NA)
#dev.off()


```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

