---
title: "Experiment 5 adults' beliefs about animal knowledge vs. human knowledge"
output: html_notebook
---


```{r}
rm(list = ls(all = TRUE))
#load needed libraries
library(FactoMineR)
library(psych)
library(gdata)
library(data.table)
library(tidyr)
library(reshape2)
library(ggfortify)
library(qdapTools)
library(lm.beta)

##### change current group to select dataset
currentgroup = c("US","JP")
currentcondition = c("human","animal")

#human-animal comparison
read <- c("how.wash")
sensory <- c("how.see")
core <- c("how.objperm","how.number","how.smnum","how.gaze","how.angle","how.color","how.depth","how.face")
types <- c("read","sensory","core")
allitems<-c("wash","objperm","number","smnum","gaze","angle","color","depth","face","see")
allhows <- c("how.wash","how.objperm","how.number","how.smnum","how.gaze","how.angle","how.color","how.depth","how.face","how.see")
#######


## prep; load data files & set parameters
masterdata  = read.table(file = "/Users/jennywang/Google Drive/Museum/mathitude/data/alternative analyses/mathitudemaster jp.csv", sep=",",header=TRUE, na.strings="")
masterdata_t = masterdata
masterdata_t[,24:37]=(as.numeric(masterdata[,24:37]=="T"|masterdata[,24:37]=="O"))

cols<- c(a.born="royalblue1",b.mature="skyblue2",c.teach="darkorange1",d.observe="orange")

### current analysis target and dataloading
data = subset(masterdata,masterdata$Group %in% currentgroup)
data_t = subset(masterdata_t,masterdata_t$Group %in% currentgroup)
data = subset(data,data$Condition %in% currentcondition)
data_t = subset(data_t,data_t$Condition %in% currentcondition)



```

```{r}
# ## PCA ######### ########### cluster analysis ###########
# pcadata=data_t[,24:33] #mturk how
# pcadata=na.omit(pcadata)
# pcadata=t(pcadata)
# autoplot(prcomp(pcadata), label=TRUE)

```

```{r}
############################## non-parametric analyses #########
data.summ <- cbind(data[,1:7],data[,c(37, 27, 26, 36, 35, 34, 31, 30, 29, 33)])
data.summ <- melt(data.summ,id.vars=1:7)
data.summ$value = as.character(data.summ$value)
data.summ$Item = rep("how",nrow(data.summ))
for (i in c(1:nrow(data.summ))){
  if(data.summ$variable[i]=="how.wash"){
    data.summ$Item[i]=as.character(data.summ$variable[i])
  }else if(data.summ$variable[i]%in%c("how.see","how.hear")){
    data.summ$Item[i]="how.sense"
  }else{
    data.summ$Item[i]="how.core"
  }
}
data.summ$Group = as.factor(as.character(data.summ$Group))
data.summ$Condition = as.factor(as.character(data.summ$Condition))

## group comparison using chi squares
chisqsave = data.frame(files=NULL)
for(i in allhows){
  temp.count = subset(data.summ,data.summ$variable==i)[,c(7,9)]
  temp.count$value = (temp.count$value=="O"|temp.count$value=="T")
  temp.table = table(temp.count)
  temp.chisq = cbind(chisq.test(temp.table)$statistic,chisq.test(temp.table)$p.value)
  chisqsave=rbind(chisqsave,temp.chisq)
}
rownames(chisqsave)=allhows
colnames(chisqsave)=c("chisq","p")

data$Group=as.factor(as.character(data$Group))
count.when.see = data[,c(1,19)]
#change column number; 19=see 23=wash
#table.when.see=table(count.when.see)
#chisq.test(table.when.see)

chisqsave

```

```{r}
how.summ = data_t[,1:9]
output = data.frame(files=NULL)
summ.output = data.frame(files=NULL)
dat_w = data_t[,c(23,13,12,22,21,20, 17, 16, 15, 19)]
dat_h = data_t[,c(37, 27, 26, 36, 35, 34, 31, 30, 29, 33)]

for(i in c(1:nrow(data_t))){
  how.sub = how.summ[i,]
  sum.sub = as.data.frame(lapply(how.sub, rep, 3))
  how.sub = as.data.frame(lapply(how.sub, rep, 10))
  for (k in c(1:10)){
      how.sub$Item[k] <- allhows[k]
      how.sub$How[k] <- dat_h[i,k]
      how.sub$When[k] <- dat_w[i,k]
  }
  for(j in c(1:3)){
    sum.sub$Type[j]<-types[j]
    sum.sub$How[j] <- mean(how.sub$How[how.sub$Item %in% eval(parse(text = types[j]))],na.rm=TRUE)
    sum.sub$When[j] <- mean(how.sub$When[how.sub$Item %in% eval(parse(text = types[j]))],na.rm=TRUE)
  }
  output = rbind(output,how.sub)
  summ.output = rbind(summ.output,sum.sub)
}

summ.output$Condition = as.factor(as.character(summ.output$Condition))
summ.output$Type = as.factor(as.character(summ.output$Type))
summ.output$Gender = as.factor(as.character(summ.output$Gender))
summ.output$Parent = as.factor(as.character(summ.output$Parent))
summ.output$SubID = as.factor(as.character(summ.output$SubID))
summ.output$Education = as.factor(as.character(as.integer(summ.output$Education)>2)) #all academics had college+ degree, so changed to graduate+

descr.how <-describeBy(summ.output$How,list(summ.output$Type,summ.output$Group,summ.output$Condition),na.rm=TRUE,mat=TRUE)
descr.how$confIV1 = descr.how$mean-1.96*descr.how$se
descr.how$confIV2 = descr.how$mean+1.96*descr.how$se

descr.how

```

```{r}
descr.when <-describeBy(summ.output$When,list(summ.output$Type,summ.output$Group,summ.output$Condition),na.rm=TRUE,mat=TRUE)
descr.when$confIV1 = descr.when$mean-1.96*descr.when$se
descr.when$confIV2 = descr.when$mean+1.96*descr.when$se
descr.when

```



```{r}
output.core=subset(summ.output,summ.output$Type=="core")
t.test(output.core$How,mu=0.5)

```

```{r}
######### linear regression ANIMAL ###########
fit.lm <- lm(How~Gender+Age+Group+Condition,data=output.core)
lm.beta(fit.lm)
```

```{r}
summary(fit.lm)
```

```{r}
fit.lm <- lm(When~Gender+Age+Group+Condition,data=output.core)
lm.beta(fit.lm)
```

```{r}
summary(fit.lm)

```

```{r}

summ.w <- describeBy(output.core$When,list(output.core$Group,output.core$Condition),na.rm=TRUE,mat=TRUE)
summ.w$confIV1 = summ.w$mean-1.96*summ.w$se
summ.w$confIV2 = summ.w$mean+1.96*summ.w$se
summ.w

```






Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

