---
title: "Experiment 4 beliefs about temperament traits"
output: html_notebook
---

```{r}
rm(list = ls(all = TRUE))
#load needed libraries
library(FactoMineR)
library(psych)
library(gdata)
library(data.table)
library(tidyr)
library(reshape2)
library(ggfortify)
library(qdapTools)
library(lm.beta)

##### change current group to select dataset
currentgroup = "MT.18.JL"
currentcondition = c("1","2")

#human-animal comparison
read <- c("how.punctual")
sensory <- c("how.eyes","how.taste.smell")
core <- c("how.active","how.attentive","how.easy","how.fearful","how.smiley")
types <- c("read","sensory","core")
allitems<-c("punctual","active","attentive","easy","fearful","smiley","taste.smell","eyes")
allhows <- c("how.punctual","how.active","how.attentive","how.easy","how.fearful","how.smiley","how.taste.smell","how.eyes")
#######


## prep; load data files & set parameters
masterdata  = read.table(file = "/Users/jennywang/Google Drive/Museum/mathitude/data/alternative analyses/temperamentmaster.csv", sep=",",header=TRUE, na.strings="")
masterdata_t = masterdata
masterdata_t[,24:37]=(as.numeric(masterdata[,24:37]=="T"|masterdata[,24:37]=="O"))

empirical = c(4,4,1,1,1,1,1,1,1,1)
cols<- c(a.born="royalblue1",b.mature="skyblue2",c.teach="darkorange1",d.observe="orange")

### current analysis target and dataloading
data = subset(masterdata,masterdata$Group==currentgroup)
data_t = subset(masterdata_t,masterdata_t$Group==currentgroup)

#overall descriptives
des_m = describeBy(data[10:23],group=NULL,na.rm=TRUE)
dat_m = data[,24:37]
table_m= mtabulate(dat_m)
time_m = des_m
how_m = table_m/rowSums(table_m,na.rm=FALSE)
colnames(how_m) <- c("b.mature","a.born","d.observe","c.teach")
summ_m = cbind(how_m,time_m)
summ_m$Category.num = c(11,10,9,8,6,4,3,2,1,1,7,5,12,13)
summ_m<-summ_m[-c(9,11,12),]
summ_m<-summ_m[order(summ_m$Category.num),]
summ_m$mean.estimate = 0.13*exp(0.78*summ_m$mean)
summ_m$se.estimate = 0.13*exp(0.78*summ_m$se)
summ_m$confIV1.estimate = summ_m$mean.estimate-1.96*summ_m$se.estimate
summ_m$confIV2.estimate = summ_m$mean.estimate+1.96*summ_m$se.estimate
summ_m[,-c(1:18)]

```

```{r}
# ## PCA ######### ########### cluster analysis ###########
pcadata=data_t[,20:29] #mturk how
pcadata=na.omit(pcadata)
pcadata=t(pcadata)
autoplot(prcomp(pcadata), label=TRUE)
```


```{r}
## calculate group stats for sensory, core knowledge, and read
how.summ = data_t[,1:9]
output = data.frame(files=NULL)
summ.output = data.frame(files=NULL)

for(i in c(1:nrow(data_t))){
  how.sub = how.summ[i,]
  sum.sub = as.data.frame(lapply(how.sub, rep, 3))
  how.sub = as.data.frame(lapply(how.sub, rep, 8))
  for (k in c(1:8)){
    how.sub$Item[k] <- allhows[k]
    how.sub$How[k] <- data_t[[paste("how.",allitems[k],sep="")]][i]
    how.sub$When[k] <- data_t[[paste("when.",allitems[k],sep="")]][i]
    how.sub$When.estimate[k]<-0.13*exp(0.78*how.sub$When[k])
  }
  for(j in c(1:3)){
    sum.sub$Type[j]<-types[j]
    sum.sub$How[j] <- mean(how.sub$How[how.sub$Item %in% eval(parse(text = types[j]))],na.rm=TRUE)
    sum.sub$When[j] <- mean(how.sub$When[how.sub$Item %in% eval(parse(text = types[j]))],na.rm=TRUE)
    sum.sub$When.estimate[j]<-mean(how.sub$When.estimate[how.sub$Item %in% eval(parse(text = types[j]))],na.rm=TRUE)
  }
  output = rbind(output,how.sub)
  summ.output = rbind(summ.output,sum.sub)
}

summ.output$Condition = as.factor(as.character(summ.output$Condition))
summ.output$Type = as.factor(as.character(summ.output$Type))
summ.output$Gender = as.factor(as.character(summ.output$Gender))
summ.output$Parent = as.factor(as.character(summ.output$Parent))
summ.output$SubID = as.factor(as.character(summ.output$SubID))
summ.output$Education = as.factor(as.character(summ.output$Education>1))

descr.how <-describeBy(summ.output$How,list(summ.output$Type),na.rm=TRUE,mat=TRUE)
descr.how$confIV1 = descr.how$mean-1.96*descr.how$se
descr.how$confIV2 = descr.how$mean+1.96*descr.how$se

descr.how[,c(2,5,16,17)]


```

```{r}

descr.when <-describeBy(summ.output$When,list(summ.output$Type),na.rm=TRUE,mat=TRUE)
descr.when$confIV1 = descr.when$mean-1.96*descr.when$se
descr.when$confIV2 = descr.when$mean+1.96*descr.when$se
descr.when$mean.estimate = 0.13*exp(0.78*descr.when$mean)
descr.when$se.estimate = 0.13*exp(0.78*descr.when$se)
descr.when$confIV1.estimate = descr.when$mean.estimate-1.96*descr.when$se.estimate
descr.when$confIV2.estimate = descr.when$mean.estimate+1.96*descr.when$se.estimate

descr.when[,c(2,18:21)]

```

```{r}
output.core=subset(summ.output,summ.output$Type=="core")
t.test(output.core$How,mu=0.5)

```

```{r}
######### linear regression ###########
fit.lm <- lm(When.estimate~Gender+Age+Education+Parent,data=output.core)
lm.beta(fit.lm)
```

```{r}
summary(fit.lm)
```

```{r}

summ.w <- describeBy(output.core$When.estimate,output.core$Gender,na.rm=TRUE,mat=TRUE)
summ.w$confIV1 = summ.w$mean-1.96*summ.w$se
summ.w$confIV2 = summ.w$mean+1.96*summ.w$se
summ.w[,c(2,5,16,17)]


```

```{r}
summ.w <- describeBy(output.core$When.estimate,output.core$Education,na.rm=TRUE,mat=TRUE)
summ.w$confIV1 = summ.w$mean-1.96*summ.w$se
summ.w$confIV2 = summ.w$mean+1.96*summ.w$se
summ.w[,c(2,5,16,17)]


```

```{r}

fit.lm <- lm(How~Gender+Age+Education+Parent,data=output.core)
lm.beta(fit.lm)
```

```{r}
summary(fit.lm)

```

```{r}
summ.h <- describeBy(output.core$How,output.core$Gender,na.rm=TRUE,mat=TRUE)
summ.h$confIV1 = summ.h$mean-1.96*summ.h$se
summ.h$confIV2 = summ.h$mean+1.96*summ.h$se
summ.h[,c(2,5,16,17)]
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

