---
title: "Experiment 2 entering age in number and use slider to indicate %genes vs. experience"
output: html_notebook
---

```{r}
rm(list = ls(all = TRUE))
#load needed libraries
library(FactoMineR)
library(psych)
library(gdata)
library(data.table)
library(tidyr)
library(reshape2)
library(ggfortify)
library(qdapTools)
library(lm.beta)

data_r  = read.table(file = "/Users/jennywang/Google Drive/Museum/mathitude/data/alternative analyses/mathitude_slider.csv", sep=",",header=TRUE, na.strings="")

read <- c("how.read")
sensory <- c("how.see","how.hear")
core <- c("how.color","how.depth","how.face","how.gravity","how.objperm","how.number","how.help")
types <- c("read","sensory","core")

allitem = c("see","hear","color","depth","face","gravity","objperm","number","help","read")

data_t=data_r[,1:5]
for(i in allitem){
  data_r[[paste("when.",i,sep="")]] = data_r[[paste("when.",i,".y",sep="")]]+data_r[[paste("when.",i,".m",sep="")]]/12
  data_t[[paste("how.",i,sep="")]]=data_r[[paste("how.",i,sep="")]]
}

for(i in allitem){
  data_t[[paste("when.",i,sep="")]]=data_r[[paste("when.",i,sep="")]]
}

how_m = describe(data_t[6:15])[,c(3,13)]
time_m = describe(data_t[16:25])[,c(3,13)]
rownames(time_m) <- allitem
summ_m = cbind(time_m,how_m)

### for plotting: summ_m$mean = 1.28*log(mean)+2.59
summ_m$confIV1 = summ_m$mean-1.96*summ_m$se
summ_m$confIV2 = summ_m$mean+1.96*summ_m$se
summ_m


```

```{r}
# ## PCA ######### ########### cluster analysis ###########
pcadata=data_t[,6:15] #mturk how
pcadata=na.omit(pcadata)
pcadata=t(pcadata)
autoplot(prcomp(pcadata), label=TRUE)
```


```{r}
## calculate group stats for sensory, core knowledge, and read
data_g=data_t
how.summ=data_t[,c(1:5)]
output = data.frame(files=NULL)
summ.output = data.frame(files=NULL)

for(i in c(1:nrow(data_g))){
  how.sub = how.summ[i,]
  sum.sub = as.data.frame(lapply(how.sub, rep, 3))
  how.sub = as.data.frame(lapply(how.sub, rep, 10))
  for (k in c(6:15)){
    how.sub$Item[k-5] <- colnames(data_g)[k]
    how.sub$How[k-5] <- data_g[i,k]
    how.sub$When[k-5] <- data_g[i,k+10]
  }
  for(j in c(1:3)){
    sum.sub$Type[j]<-types[j]
    sum.sub$How[j] <- mean(how.sub$How[how.sub$Item %in% eval(parse(text = types[j]))],na.rm=TRUE)
    sum.sub$When[j] <- mean(how.sub$When[how.sub$Item %in% eval(parse(text = types[j]))],na.rm=TRUE)
  }
  output = rbind(output,how.sub)
  summ.output = rbind(summ.output,sum.sub)
}

summ.output$subID = as.factor(as.character(summ.output$subID))
summ.output$Gender = as.factor(as.character(summ.output$Gender))
summ.output$parent = as.factor(as.character(summ.output$parent))
summ.output$Education = as.factor(as.character(summ.output$Education>1))

descr.how <-describeBy(summ.output$How,list(summ.output$Type),na.rm=TRUE,mat=TRUE)
descr.how$confIV1 = descr.how$mean-1.96*descr.how$se
descr.how$confIV2 = descr.how$mean+1.96*descr.how$se

descr.how[,c(2,5,16,17)]


```

```{r}

descr.when <-describeBy(summ.output$When,list(summ.output$Type),na.rm=TRUE,mat=TRUE)
descr.when$confIV1 = descr.when$mean-1.96*descr.when$se
descr.when$confIV2 = descr.when$mean+1.96*descr.when$se

descr.when[,c(2,5,16,17)]
```

```{r}
output.core=subset(summ.output,summ.output$Type=="core")
t.test(output.core$How,mu=0.5)

```

```{r}
######### linear regression ###########
output.core=na.omit(output.core)
output.core=subset(output.core,output.core$Gender!="Other")
fit.lm <- lm(When~Gender+Age+Education+parent,data=output.core)
lm.beta(fit.lm)
```

```{r}
summary(fit.lm)
```

```{r}

summ.w <- describeBy(output.core$When,output.core$Gender,na.rm=TRUE,mat=TRUE)
summ.w$confIV1 = summ.w$mean-1.96*summ.w$se
summ.w$confIV2 = summ.w$mean+1.96*summ.w$se

summ.w[,c(2,5,16,17)]


```

```{r}

fit.lm <- lm(How~Gender+Age+Education+parent,data=output.core)
lm.beta(fit.lm)
```

```{r}
summary(fit.lm)

```

```{r}
summ.h <- describeBy(output.core$How,output.core$Gender,na.rm=TRUE,mat=TRUE)
summ.h$confIV1 = summ.h$mean-1.96*summ.h$se
summ.h$confIV2 = summ.h$mean+1.96*summ.h$se
summ.h[,c(2,5,16,17)]
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

